Understanding Supersymmetry

### 2022-12-28 HW-Gravity/gravity1/gravity1.tex
Fix minor issues on AdS geodesics
Add misc fixes & updates

	On the other hand, $V^\mu$ should be properly normalized, therefore:
	\begin{equation}
	\begin{gathered}
		\norm{V}^2
		= g_{IJ} V^I V^J
		= \frac{(V^z)^2}{z^2} + z^2 p^2
		= \delta = 0,\pm 1,
%	\quad
%		p^2 = p_\mu p^\mu = \eta_{\mu\nu} p^\mu p^\nu,
	\label{eq:tangent_norm}
	\end{gathered}
	\end{equation}
	For $p^2 = 0$, we have $
		\norm{V}^2
		= \frac{(V^z)^2}{z^2}
		\ge 0
	$, thus $\gamma$ can be either spacelike or null, but not timelike. In fact, $
		\frac{1}{z}\dv{z}{\lambda} = 0,\pm 1
	$, along with $\dv{x^\mu}{\lambda} = z^2 p^\mu$, we obtain:
	\begin{equation}
	p^2 = 0,\qquad
	\begin{aligned}
		\text{spacelike}\colon\ &
			z(\lambda)
			= z(0)\,e^{\pm\lambda},
		&&
			x^\mu(\lambda)
			= x^\mu(0) \pm z(0)^2\,p^\mu\,
				\tfrac{
					e^{\pm 2\lambda} - 1
				}{2}, \\
		\text{null}\colon\ &
			z(\lambda)
			= z(0),
		&&
			x^\mu(\lambda)
			= x^\mu(0) + z(0)^2\,p^\mu \lambda,
	\end{aligned}
	\label{eq:null_type}
	\end{equation}

@@

	In summary, there are 3 types of spacelike geodesics in Poincar\'e AdS, which closely resemble the 3 types of conic sections:
	\begin{enumerate}
	\item $p^2 = 0$: parabolic, given in \eqref{eq:null_type}, with one end going to $z\to 0$ and the other end going to $z\to\infty$; it takes infinite proper length $\lambda$ for it to reach $0$ or $\infty$. 
	\item $p^2 > 0$: hyperbolic, given in \eqref{eq:unified_geodesic} and \eqref{eq:hyperbolic}, also with one end going to $z\to 0$ and the other end going to $z\to\infty$, but it reaches $\infty$ within finite $\lambda$. 
	\item $p^2 > 0$: elliptic, given in \eqref{eq:unified_geodesic} and \eqref{eq:elliptic}, with both ends going to $z\to 0$, and it takes infinite proper length $\lambda$ for it to reach either end. 
	\end{enumerate}

	Now consider two points $x_1,x_2$ near the boundary $z = \epsilon$ connected by a spacelike geodesic $\gamma$. This can only be the ``elliptic type'' discussed above. We have:
	\begin{equation}
		x^\mu
		= a^\mu \pm \widehat{p}^\mu
			\sqrt{\pqty{\frac{L}{2}}^{\!\!2} - z^2},
	\quad
		z^2 + (x - a)^2
		= \pqty{\frac{L}{2}}^{\!\!2},
	\end{equation}
	\\[-1.5\baselineskip]
	\begin{equation}
		a = \frac{x_1 + x_2}{2},
	\quad
		\widehat{p} \propto x_2 - x_1
	\end{equation}
	It's length is then given by:
	\begin{equation}
	\begin{aligned}
		A
		&= \int_{z=-\epsilon}^{z=\epsilon}
			\frac{\dd{x}^2 + \dd{z}^2}{z^2} \\
		&= \int_{-\Lambda}^{\Lambda}
			\frac{
				(\dd{\tanh\lambda})^2
				+ (\dd{\sech\lambda})^2
			}{(\sech\lambda)^2},
		\quad \Lambda
			= \cosh^{-1} (\tfrac{L}{2\epsilon}) \\
		&= \int_{-\Lambda}^{\Lambda}
			\dd{\lambda}
		= 2\Lambda
		= 2\cosh^{-1} \pqty{\frac{L}{2\epsilon}}
		\sim 2\log \frac{L}{\epsilon},
	\quad \epsilon \to 0
	\end{aligned}
	\end{equation}

>>>>

	On the other hand, $V^\mu$ should be properly normalized, therefore:
	\begin{equation}
	\begin{gathered}
		\norm{V}^2
		= g_{IJ} V^I V^J
		= \frac{(V^z)^2}{z^2} + z^2 p^2
		= \delta = 0,\pm 1,
%	\quad
%		p^2 = p_\mu p^\mu = \eta_{\mu\nu} p^\mu p^\nu,
	\label{eq:tangent_norm}
	\end{gathered}
	\end{equation}
	For $p^2 = 0$, we have $
		\norm{V}^2
		= \frac{(V^z)^2}{z^2}
		\ge 0
	$, thus $\gamma$ can be either spacelike or null, but not timelike. In fact, we have $
		\frac{V^z}{z}
		= \frac{1}{z}\dv{z}{\lambda}
		= 0,\pm 1
	$; along with $\dv{x^\mu}{\lambda} = z^2 p^\mu$, we obtain:
	\begin{equation}
	p^2 = 0,\qquad
	\begin{aligned}
		\text{spacelike}\colon\ &
			z(\lambda)
			= z(0)\,e^{\pm\lambda},
		&&
			x^\mu(\lambda)
			= x^\mu(0) \pm z(0)^2\,p^\mu\,
				\tfrac{
					e^{\pm 2\lambda} - 1
				}{2}, \\
		\text{null}\colon\ &
			z(\lambda)
			= z(0),
		&&
			x^\mu(\lambda)
			= x^\mu(0) + z(0)^2\,p^\mu \lambda,
	\end{aligned}
	\label{eq:null_type}
	\end{equation}

@@

	In summary, there are 3 types of spacelike geodesics in Poincar\'e AdS, which closely resemble the 3 types of conic sections:
	\begin{enumerate}
	\item $p^2 = 0$: parabolic, given in \eqref{eq:null_type}, with one end going to $z\to 0$ and the other end going to $z\to\infty$; it takes infinite proper length $\lambda$ for it to reach $0$ or $\infty$. 
	\item $p^2 < 0$: hyperbolic, given in \eqref{eq:unified_geodesic} and \eqref{eq:hyperbolic}, also with one end going to $z\to 0$ and the other end going to $z\to\infty$, but it reaches $\infty$ within finite $\lambda$. 
	\item $p^2 > 0$: elliptic, given in \eqref{eq:unified_geodesic} and \eqref{eq:elliptic}, with both ends going to $z\to 0$, and it takes infinite proper length $\lambda$ for it to reach either end. 
	\end{enumerate}

	Now consider two points $x_1,x_2$ near the boundary $z = \epsilon$ connected by a spacelike geodesic $\gamma$. This can only be the ``elliptic type'' discussed above. We have:
	\begin{equation}
		x^\mu
		= a^\mu \pm \widehat{p}^\mu
			\sqrt{\pqty{\frac{L}{2}}^{\!\!2} - z^2},
	\quad
		z^2 + (x - a)^2
		= \pqty{\frac{L}{2}}^{\!\!2},
	\end{equation}
	\\[-1.5\baselineskip]
	\begin{equation}
		a = \frac{x_1 + x_2}{2},
	\quad
		\widehat{p} \propto x_2 - x_1
	\end{equation}
	It's length is then given by:
	\begin{equation}
	\begin{aligned}
		A
		&= \int_{z\ge\epsilon}
			\sqrt{\frac{\dd{x}^2 + \dd{z}^2}{z^2}} \\
		&= \int_{\abs{\lambda} \le \Lambda} \sqrt{
			\frac{
				(\dd{\tanh\lambda})^2
				+ (\dd{\sech\lambda})^2
			}{(\sech\lambda)^2}
		},
		\quad \Lambda
			= \cosh^{-1} (\tfrac{L}{2\epsilon}) \\
		&= \int_{-\Lambda}^{\Lambda}
			\dd{\lambda}
		= 2\Lambda
		= 2\cosh^{-1} \pqty{\frac{L}{2\epsilon}}
		\sim 2\log \frac{L}{\epsilon},
	\quad \epsilon \to 0
	\end{aligned}
	\end{equation}

### 2022-12-28 alpha/SUSY/susy.tex
Add misc fixes & updates

>>>>

\subsection{Some cool facts about anomaly}
\label{subsect:anomaly}
\references{
	\begin{enumerate}[noitemsep,topsep=0pt]
	\item \textcite{Tong:2018gauge}, \S3
	\item \textcite{Schwartz:2014sze}, \S30
	\end{enumerate}
}\vspace{\parskip}

	At the classical level, a massless Dirac fermion in \textit{even} dimensions enjoys the symmetry:
	\begin{equation}
		\mrm{U}(1)_V \times \mrm{U}(1)_A
	\end{equation}
	But only a $\mrm{U}(1)$ subgroup survives after quantization of the continuum field theory. This is the so-called chiral anomaly.

	The interesting thing is that we can actually choose the surviving $\mrm{U}(1)$ subgroup. The $\mrm{U}(1)_A$ subgroup is often doomed to suffer, which is why we often don't distinguish the chiral anomaly with the so-called axial anomaly. 
	On the other hand, the $\mrm{U}(1)_V$ subgroup is usually the lucky survivor, due to its close relation with the gauge symmetry, which affects our choice of regularization schemes.

	Recall that in general, anomaly arises when it's impossible to choose a regularization scheme that is compatible with the symmetry. In usual computations of the chiral anomaly, we often assume the survival of $\mrm{U}(1)_V$, either explicitly or implicitly. 
	\begin{itemize}
	\item Let's denote the axial current as $j^\sigma$ and the vector current as $J^\mu$. When computing the triangle diagram $\vev{j^\sigma J^\mu J^\nu}$ in 4D, there is a free paramter that we can tune to regularize the loop momentum integral, which ``distributes'' the anomalous amplitude between $\pdd{\sigma} j^\sigma$ and $\pdd{\mu} J^\mu$. More precisely, the result is that $\pdd{\sigma} \vev{j^\sigma J^\mu J^\nu}$ and $\pdd{\mu} \vev{j^\sigma J^\mu J^\nu}$ cannot vanish simultaneously.

	\item Computing $\vev{j^\sigma J^\mu J^\nu}$ is equivalent to computing $\vev{j^\sigma}_A$, where $A^\mu$ is some non-dynamic background gauge field coupled to $J^\mu$. Basically\footnote{
		This is taken from \S22.3 of \textcite{Weinberg:1996kr}, Vol.\,II, where there is an extra minus sign in the front, probabaly due to a different convention for the current $j$. 
	},
	\begin{equation}
		\vev{j^\sigma}_A
		= \frac{1}{2} \int \dd[D]{x} \dd[D]{y}
			\vev{j^\sigma J^\mu(x) J^\nu(y)}\,
			A_\mu(x) A_\nu(y)
	\end{equation}
	I believe the $\frac{1}{2}$ factor here is to cancel the overcounting as we integrate over both $x$ and $y$.

	\item We usually compute the axial anomaly for a massless Dirac fermion. Equivalently, we can look at its components, which are a pair of left and right-handed Weyl fermions, charged $Q = \pm 1$ under $\mrm{U}(1)_A$. They each contribute half of the anomaly. To prove this, one can insert a projection matrix $\frac{1 \pm \gamma_5}{2}$ which reduces the action for a Dirac fermion to that of a Weyl fermion\footnote{
		Note that the Dirac mass term mixes left and right-handed components and will always be projected out. 
	}; see \S30.2.4 of \cite{Schwartz:2014sze}.

	In general, we can consider a series of Weyl fermions charged $Q$ under $\mrm{U}(1)_A$. Their contribution to the anomaly will be given by $\Tr Q\gamma_5$, where the trace goes over the whole representation. For the massless Dirac fermion with $Q = \pm 1$, we have:
	\begin{equation}
	\begin{aligned}
		\Tr_{\,\textsl{Dirac}} Q\gamma_5
		&= \Tr_{\,\textsl{Dirac}} \pqty{
				\frac{1 + \gamma_5}{2}\,Q
				- \frac{1 - \gamma_5}{2}\,Q
			} \\
		&= \Tr_{\,\textsl{Dirac}} \pqty{
				\frac{1 + \gamma_5}{2}\,(+1)
				- \frac{1 - \gamma_5}{2}\,(-1)
			}
		= \frac{1}{2} + \frac{1}{2}
		= 1
	\end{aligned}
	\end{equation}

	\item Note that the axial $\mrm{U}(1)_A$ only exists in even dimensions, where we have a chirality matrix $\Gamma$ like $\gamma_5$, and we have Weyl spinors with definite chiralities; see \S1.1. In odd dimensions there are only (symplectic) Majorana spinors, so we can't even define $\mrm{U}(1)_A$ at the classical level.

	On the other hand, massless Majorana spinors in even dimensions do admit $\mrm{U}(1)_A$ just like massless Dirac spinors, but it must be $\mrm{U}(1)_V$ neutral due to the reality condition\footnote{
		It does have a $\mbb{Z}_2$ symmetry which can be understood as the remnant of the $\mrm{U}(1)_V$ at $\theta = \pi$, where $e^{i\theta} = -1$. This is quite similar to the fermion number symmetry $(-1)^F$ discussed in \S1.2. 
	}.
